Convective Penetration Paper Outline

### 2021-05-06 notes/outline/outline.tex
adds some sources to intro, etc.

\newcommand{\aap}{A\&A}
\newcommand{\apj}{ApJ}
\newcommand{\apjl}{ApJL}
\newcommand{\mnras}{MNRAS}
\newcommand{\araa}{Annual Review of Astronomy and Astrophysics}

@@

\section{Intro \& Background}
\begin{itemize}
\item Observational \& Theoretical context: ``convective overshoot'' and the problems it relates to.
Include sources on e.g., stellar Lithium abundances \citep[][fig 4]{pinsonneault_1997}, helioseismology \citep[][]{christensen-dalsgaard_etal_2011}, stellar evolution \& remnants \citep{higgins_vink_2020}, stellar core convection overshoot \citep{claret_torres_2018}, $\sim$every MESA paper? Other things?
\item Terminology of overshoot vs penetration.
\item Note that the state of the field has been reviewed many times by many authors \citep{marcus_etal_1983, zahn1991, browning_etal_2004, rogers_etal_2006, viallet_etal_2015, korre_etal_2019}.
\item Miscellaneous theoretical or semianalytical arguments or models \citep{marcus_etal_1983, zahn1991, hurlburt_etal_1994, rempel2004, canuto2011, viallet_etal_2015, korre_etal_2019} (also Roxburgh?).
\item Briefly review simulations:
\begin{itemize}
\item ``Early'' simulations of e.g., plumes \citep{schmitt_etal_1984}.
\item Dynamical Cartesian simulations in both fully compressible and Boussinesq equation sets \citep{hurlburt_etal_1994, brummell_etal_2002, rogers_glatzmaier_2005, kapyla_etal_2007, kitiashvili_etal_2016, kapyla_etal_2017, couston_etal_2017, toppaladoddi_wettlaufer_2018}.
\item Dynamical spherical geometry 2D or 3D simulations (fully compressible, anelastic, boussinesq, some solar-like, some not) \citep{browning_etal_2004, rogers_etal_2006, brun_etal_2017, pratt_etal_2017, dietrich_wicht_2018}
\end{itemize}
\item Zahn's energetics arguments and the various times it has cropped up in the literature \citep{zahn1991, hurlburt_etal_1994, rempel2004, rogers_etal_2006}.
\item Say very clearly that \emph{the penetration depth depends on how steeply the radiative flux changes with depth} (and also convective structures).
Say that we're going to present simulations which agree with this.
\end{itemize}

@@

\subsection{Measured penetration zone scalings}
\begin{itemize}
\item Here we show that the predicted $\mathcal{P}$ scalings do a pretty good job.
This will include some parameter space plots (probably all in one figure) that show:
\begin{itemize}
\item $\delta_P$ depends on $\mathcal{P}$.
\item $\delta_P$ does not really depend strongly on $\mathcal{S}$ or $\mathcal{R}$.
\end{itemize}
\item Mention that 2D simulations produce more pronounced PZs (larger by a factor of $\sim 2$) but similar scalings with theory; we choose to omit 2D results and focus on more realistic 3D results.
\item our theory has $\delta_P = A \mathcal{P}$ (for erf sims) and $\delta_P = B \mathcal{P}^{1/2}$; we should report good-fits for $A$ and $B$.
These can be plugged directly into MESA as first guesses as the penetration depth there.
\end{itemize}

>>>>

\newcommand{\aap}{A\&A}
\newcommand{\apj}{ApJ}
\newcommand{\apjl}{ApJL}
\newcommand{\apjs}{ApJS}
\newcommand{\apss}{Astrophysics and Space Science}
\newcommand{\mnras}{MNRAS}
\newcommand{\araa}{Annual Review of Astronomy and Astrophysics}

@@

\section{Intro \& Background}
\begin{itemize}
\item Observational \& Theoretical context: ``convective overshoot'' and the problems it relates to.
Include sources on e.g., 
\begin{itemize}
\item stellar Lithium abundances \citep[][fig 4]{pinsonneault_1997}, 
\item solar modeling problem \citep{basu_antia_2004, bahcall_etal_2005, vinyoles_etal_2017, asplund_etal_2021},
\item helioseismology \citep[][]{christensen-dalsgaard_etal_2011},
\item stellar evolution \& remnants \citep{higgins_vink_2020}, 
\\item stellar core convection overshoot \citep{claret_torres_2018}, 
\item parameterizations \citep{shaviv_salpeter_1973, maeder1975, herwig2000} and ``convective boundaries'' in MESA papers \citep{paxton_etal_2011, paxton_etal_2013, paxton_etal_2018, paxton_etal_2019}. 
\item Other things?
\end{itemize}
\item Terminology of overshoot vs penetration.
\item Note that the state of the field has been reviewed many times by many authors \citep{marcus_etal_1983, zahn1991, browning_etal_2004, rogers_etal_2006, viallet_etal_2015, korre_etal_2019}.
We will do a brief review but these are additional resources.
\item Mention miscellaneous theoretical or semianalytical arguments or models \citep{roxburgh1965, roxburgh1978, roxburgh1989, roxburgh1992, roxburgh1998, marcus_etal_1983, zahn1991, hurlburt_etal_1994, rempel2004, canuto2011, viallet_etal_2015, korre_etal_2019}.
\item Briefly review simulations:
\begin{itemize}
\item ``Early'' simulations of e.g., plumes \citep{schmitt_etal_1984}.
\item Dynamical Cartesian simulations in both fully compressible and Boussinesq equation sets \citep{hurlburt_etal_1994, brummell_etal_2002, rogers_glatzmaier_2005, kapyla_etal_2007, kitiashvili_etal_2016, lecoanet_etal_2016, kapyla_etal_2017, couston_etal_2017, toppaladoddi_wettlaufer_2018}.
\item Dynamical spherical geometry 2D or 3D simulations (fully compressible, anelastic, boussinesq, some solar-like, some not) \citep{browning_etal_2004, rogers_etal_2006, brun_etal_2017, pratt_etal_2017, dietrich_wicht_2018}
\end{itemize}
\item Zahn's energetics arguments and the various times it has cropped up in the literature \citep{zahn1991, hurlburt_etal_1994, rempel2004, rogers_etal_2006}.
\item Say very clearly that \emph{the penetration depth depends on how steeply the radiative flux changes with depth} (and also convective structures).
Say that we're going to present simulations which agree with this.
\end{itemize}

@@

\subsection{Measured penetration zone scalings}
\begin{itemize}
\item Profile verification of theory.
Does $W$ go from $W_0$ to $\mathcal{O}(0)$ at the top of the PZ?
Is it an e-folding?
Also how does the rms Pe or Re scale with height?
Does Zahn's ``thermal adjustment layer'' with Pe $\sim$ 1 hold in the PZ-RZ transition?
\item Show that the predicted $\mathcal{P}$ scalings do a pretty good job.
This will include some parameter space plots (probably all in one figure) that show:
\begin{itemize}
\item $\delta_P$ depends on $\mathcal{P}$.
\item $\delta_P$ does not really depend strongly on $\mathcal{S}$ or $\mathcal{R}$.
\end{itemize}
\item Mention that 2D simulations produce more pronounced PZs (larger by a factor of $\sim 2$) but similar scalings with theory; we choose to omit 2D results and focus on more realistic 3D results.
\item our theory has $\delta_P = A \mathcal{P}$ (for erf sims) and $\delta_P = B \mathcal{P}^{1/2}$; we should report good-fits for $A$ and $B$.
These can be plugged directly into MESA as first guesses as the penetration depth there.
\end{itemize}
